Internet Routing Security

### 2019-12-02 paper.tex
Trim a few more words; still over

\section{Internet Routing Operation}
In order to reach services like Youtube, users must be provided with a path to reach the service.  Youtube may have a set of IP addresses to allow users to connect to, but there are still two technical challenges:
\begin{enumerate}
 \item Youtube needs to announce where those IP addresses exist in the Internet
 \item The global Internet must find the paths to reach Youtube
\end{enumerate}
The \emph{Border Gateway Protocol (BGP)} is used to solve these problems, and its operation is illustrated in Figure \ref{fig:bgp-ops}.  Continuing with the Youtube example, Youtube announces those addresses as an IP prefix\footnote{An IP prefix could be one of the blocks assigned to the organization, or it could be a contiguous subset of IP addresses within that block.} into its ISP, which takes care of challenge 1.

In that same announcement, Youtube also announces its ASN.  When Youtube's ISP connects to another network, it appends its own ASN after Youtube's ASN to make an ordered list that describes a path.  This process continues throughout the Internet, allowing for each network to know which path or paths it can take to reach Youtube.  These paths, known as \emph{AS paths}, all begin with Youtube's ASN, which maps Youtube's ASN to it's IP space in the global Internet.  These AS paths are used to address challenge 2.

If there are multiple paths to a target IP address, BGP uses a multi-step decision process to determine which route is preferred\footnote{The BGP decision process is not standardized, and it may vary across different implementations.  Many implementations are very similar.}.  One of the most critical factors in the decision process for ISPs is the AS path length.  The path with the shortest AS path length to a given destination is often the preferred route.

\section{BGP Hijacking}
Understanding how BGP operates, it is now helpful to revisit the Youtube outage previously introduced.  Pakistan's state run network had attempted to take all traffic in its network destined for Youtube's IP prefixes and drop it.  By mistake, this change in their internal network was announced to the rest of the Internet via BGP.  Figure {fig:bgp-hijack} illustrates what may have happened for some users who experienced a Youtube outage.  This was an example of \emph{BGP hijacking}, and it illustrates that the BGP has an inherent weakness: the receiver of the BGP announcement trusts the sender of the announcement, who in turn trusted the sender of the previous BGP announcement, and so on.  This trust model is known as \emph{transitive trust}, and it is part of why BGP is not secure.  BGP hijacking can be unintentional, such as the Youtube example, but it can also be intentionally performed by malicious actors for data interception, eavesdropping, or denial of service.  Both intentional and unintentional BGP hijacking occur on a near-daily basis\cite{b1}.

@@

\section{BGP Hijacking Mitigation Techniques}
Multiple techniques exist to mitigate the weaknesses in BGP, each with varying effectiveness and cost.  Three techniques discussed below are \emph{Filtering}, \emph{Resource Public Key Infrastructure (RPKI)}, and \emph{BGPsec}.  Filtering has been used for a number of years, while RPKI and BGPsec are only recently seeing adoption.  A brief comparison of these models is presented in Table \ref{tab:bgp-hijacking-comparison} at the end of this chapter.

\subsection{Filtering}
Filtering is a technique to prevent propagating incorrect announcements from neighbors.  There are numerous BGP filtering methods, with two examples being AS path filtering and IP prefix filtering.  AS path filtering only allows a set of whitelisted ASNs to be sent or accepted in BGP announcements.  This is effective for ISPs near the edge of the Internet, as those ISPs can choose to only accept AS paths comprised of the organization's ASN\footnote{Organizations can similarly apply AS path filtering on egress of their announcements to avoid accidental propagation of incorrect ASNs}.  IP prefix filtering is similar to AS path filtering, only it is applied to specific whitelisted IP prefixes.  Given that BGP hijacking events are still relatively frequent, it appears that filtering alone is insufficient to prevent BGP hijacking.

\subsection{Resource Public Key Infrastructure for Origin Validation}
As noted previously, RIRs have a central mapping of IP prefixes to ASNs, and the first ASN in an ASN path should correspond to the associated IP prefix in an announcement.  Can the mapping of ASNs to IP prefixes be used to validate the origin of BGP announcements?  This approach is used by operators who uncover BGP hijacking events after they have occurred, and it is also the concept behind Resource Public Key Infrastructure (RPKI).  RPKI attempts to automate this approach by having the RIRs host digitally signed information, known as \emph{Route Organization Authorizations (ROAs)} confirming that an AS has the authority to announce an IP prefix.  Different RIRs implement RPKI processes differently, but one example is presented in Figure \ref{fig:rpki-assignment}.  Figure \ref{fig:rpki-ops} illustrates how a BGP router can validate the origin of an announced prefix.

@@

\subsection{BGPsec}
RPKI prevents many BGP hijacking issues, but it doesn't resolve all of them.  Consider malicious actors who want to intercept data destined for Youtube.  RPKI can detect the malicious network announcing it owns the Youtube IP space, but it cannot detect the case in Figure \ref{fig:bgp-intercept} of the malicious network announcing a path that passes through the malicious network but that eventually reaches Youtube, even if that path is bogus.  This is another case of BGP hijacking.

A protocol known as BGPsec attempts to mitigate this case by leveraging the RPKI infrastructure for both prefix origin validation and hop-by-hop path validation.  BGPsec replaces the AS path with a \emph{BGPsec path} and places requirements on how the path can be modified.  First, the AS performing modification can only provide its own ASN along with the ASN of the neighbor that the BGPsec announcment is being sent to.  Second, the AS originating the announcement must provide a signature using the organization's RPKI private key.  Recipients of a BGPsec announcement can validate the ASNs in the BGPsec path by checking the associated signatures against the ROA database.  Figure \ref{fig:bgpsec-ops} illustrates BGPsec operations.

\section{Conclusion}
This chapter illustrated the key weakness of transitive trust in the Internet routing protocol known as BGP, and it showed how this weakness can be exploited through BGP hijacking.  Multiple mitigation techniques for this weakness were introduced, including traditional approaches such filtering as well as newer approaches such as RPKI for origin validation and BGPsec.  BGP hijacking has been shown to occur on a near-daily basis, and thus the traditional filtering methods were shown to be insufficient to address the BGP hijacking problem at Internet scale.

>>>>

\section{Internet Routing Operation}
In order to reach services like Youtube, users must be provided with a network path to reach the service.  Youtube may have a set of IP addresses for users to connect, but there are still two challenges:
\begin{enumerate}
 \item Youtube needs to announce where those IP addresses exist in the Internet
 \item The Internet must find paths to reach Youtube
\end{enumerate}
The \emph{Border Gateway Protocol (BGP)} is used to solve these problems, as illustrated in Figure \ref{fig:bgp-ops}.  Continuing with the Youtube example, Youtube announces its addresses as an IP prefix\footnote{An IP prefix could be one of the blocks assigned to the organization, or it could be a contiguous subset of IP addresses within that block.} into its ISP, which resolves challenge 1.

In that same announcement, Youtube also announces its ASN.  When Youtube's ISP connects to another network, it appends its own ASN after Youtube's ASN to make an ordered list that describes a path.  This process continues throughout the Internet, allowing for each network to know which paths it can take to reach Youtube.  These paths, known as \emph{AS paths}, all begin with Youtube's ASN, which maps Youtube's ASN to its IP space in the global Internet.  These AS paths are used to address challenge 2.

If there are multiple paths to a target IP address, BGP uses a multi-step decision process to determine which route is preferred\footnote{The BGP decision process is not standardized, and it may vary across different implementations.  Many implementations are very similar.}.  The route with the shortest AS path length for a given destination is often the preferred route.

\section{BGP Hijacking}
With an understanding of how BGP operates, it is helpful to revisit the Youtube outage previously introduced.  Pakistan's state-run network had attempted to take all traffic in its network destined for Youtube's IP prefixes and drop it.  By mistake, this change in their internal network was announced to the rest of the Internet via BGP.  Figure {fig:bgp-hijack} illustrates what may have happened for some users who experienced a Youtube outage.  This was an example of \emph{BGP hijacking}, and it highlights a weakness in BGP: the receiver of the BGP announcement trusts the sender of the announcement, who trusted the sender of the previous BGP announcement, and so on.  This trust model is known as \emph{transitive trust}, and it is part of why BGP is not secure.  BGP hijacking can be unintentional, such as the Youtube example, but it can also be intentionally performed by malicious actors for data interception, eavesdropping, or denial of service.  Both intentional and unintentional BGP hijacking occur on a near-daily basis\cite{b1}.

@@

\section{BGP Hijacking Mitigation Techniques}
Multiple techniques exist to address BGP hijacking, each with varying effectiveness and cost.  Three such techniques are \emph{Filtering}, \emph{Resource Public Key Infrastructure (RPKI)}, and \emph{BGPsec}.  Filtering has been used for a number of years, while RPKI and BGPsec are only recently seeing adoption.  A brief comparison of these techniques is presented in Table \ref{tab:bgp-hijacking-comparison} at the end of this chapter.

\subsection{Filtering}
Filtering is a technique to prevent propagating incorrect announcements from neighbors.  There are numerous BGP filtering methods, with two examples being AS path filtering and IP prefix filtering.  AS path filtering only allows a set of whitelisted ASNs to be accepted in BGP announcements.  This is effective for ISPs near the edge of the Internet, as those ISPs can choose to only accept AS paths comprised of the organization's ASN\footnote{Organizations can similarly apply AS path filtering on egress of their announcements to avoid accidental propagation of incorrect ASNs}.  IP prefix filtering is similar to AS path filtering, only it is applied to specific whitelisted IP prefixes.  Given that BGP hijacking events are still relatively frequent, filtering alone appears insufficient to prevent BGP hijacking.

\subsection{Resource Public Key Infrastructure for Origin Validation}
As noted previously, RIRs have a central mapping of IP prefixes to ASNs, and the first ASN in an AS path should correspond to the associated IP prefix in an announcement.  The mapping of ASNs to IP prefixes be used to validate the origin of BGP announcements.  This approach is used by operators who uncover BGP hijacking events after they have occurred, and it is also the concept behind Resource Public Key Infrastructure (RPKI).  RPKI automates origin validation by having the RIRs host digitally signed information, known as \emph{Route Organization Authorizations (ROAs)} confirming that an AS has authority to originate an IP prefix.  RPKI implementations vary by RIR, but one example is presented in Figure \ref{fig:rpki-assignment}.  Figure \ref{fig:rpki-ops} shows RPKI origin validation in action.

@@

\subsection{BGPsec}
RPKI prevents many cases of BGP hijacking, but it doesn't resolve all of them.  Consider malicious actors who want to intercept data destined for Youtube.  RPKI can detect a malicious network announcing it owns the Youtube IP space, but it cannot detect the case in Figure \ref{fig:bgp-intercept} of a malicious network announcing a path that passes through but does not originate from the malicious network, even if that path is fake.

A protocol known as BGPsec attempts to prevent this case by leveraging the RPKI infrastructure for full path validation.  BGPsec replaces the AS path with a \emph{BGPsec path} and places requirements on how the path can be modified.  The AS constructing the announcement can only provide its own ASN and the ASN of the BGPsec announcment recipient.  The AS constructing the announcement must provide a signature using the organization's RPKI private key.  As shown in Figure \ref{fig:bgpsec-ops}, recipients of a BGPsec announcement can validate the chain of ASNs in the BGPsec path by checking the associated signatures against the ROA database.

\section{Conclusion}
This chapter illustrated the key weakness of transitive trust in the Internet routing protocol known as BGP, and it showed how this weakness can be exploited through BGP hijacking.  Filtering, RPKI, and BGPsec were introduced as techniques for addressing BGP hijacking.
